simResults_rf

### 2024-08-08 sim_1_bross/simResults_bross.Rmd
simulation results .RMD file added & edited

---
title: "SimResults_Bross"
author: "Yang Lei"
date: "2024-07-31"
output: html_document
---

@@

# Folder "scenario"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx

@@

# Folder "scenarioER"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx

@@

# Folder "scenarioOR"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx

>>>>

---
title: "SimResults_Bross"
output: html_document
---

@@

# Folder "scenario"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

@@

# Folder "scenarioER"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

@@

# Folder "scenarioOR"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

### 2024-08-08 sim_3_lasso/simResults_lasso.Rmd
simulation results .RMD file added & edited

---
title: "SimResults_Lasso"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 5

RD_lasso <- data.frame(RD = numeric(),
                       SE = numeric())
```

@@

# Folder "scenario"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

@@

  RD_lasso[i,] <- sum.RD_lasso
  rownames(RD_lasso)[i] <- paste0("data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

@@

# Folder "scenarioER"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

@@

  RD_lasso[i+a,] <- sum.RD_lasso
  rownames(RD_lasso)[i+a] <- paste0("ER.data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.ER.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.ER.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

@@

# Folder "scenarioOR"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

@@

  RD_lasso[i+2*a,] <- sum.RD_lasso
  rownames(RD_lasso)[i+2*a] <- paste0("OR.data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.OR.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.OR.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

@@

@@

# check proxy selected by lasso for each data, print:
#   proxy_lasso.n, proxy_lasso.ER.n, or proxy_lasso.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_lasso.1
proxy_lasso.ER.3
```

>>>>

---
title: "simResults_lasso"
output: html_document
---

@@

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_lasso <- data.frame(RD = numeric(), SE = numeric())

num.proxy_lasso <- c()
```

@@

# Folder "scenario"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

@@

  RD_lasso[i,] <- sum.RD_lasso
  rownames(RD_lasso)[i] <- paste0("data.", i, "_lasso")
  num.proxy_lasso <- c(num.proxy_lasso, length(proxy_lasso))
  names(num.proxy_lasso)[i] <- paste0("data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.", i)
  assign(proxy_lasso.i, proxy_lasso)
  num.proxy_lasso.i <- paste0("num.proxy_lasso.", i)
  assign(num.proxy_lasso.i, length(proxy_lasso))
  sum.RD_lasso.i <- paste0("sum.RD_lasso.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

@@

# Folder "scenarioER"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

@@

  RD_lasso[i+a,] <- sum.RD_lasso
  rownames(RD_lasso)[i+a] <- paste0("ER.data.", i, "_lasso")
  num.proxy_lasso <- c(num.proxy_lasso, length(proxy_lasso))
  names(num.proxy_lasso)[i+a] <- paste0("ER.data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.ER.", i)
  assign(proxy_lasso.i, proxy_lasso)
  num.proxy_lasso.i <- paste0("num.proxy_lasso.ER.", i)
  assign(num.proxy_lasso.i, length(proxy_lasso))
  sum.RD_lasso.i <- paste0("sum.RD_lasso.ER.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

@@

# Folder "scenarioOR"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

@@

  RD_lasso[i+2*a,] <- sum.RD_lasso
  rownames(RD_lasso)[i+2*a] <- paste0("OR.data.", i, "_lasso")
  num.proxy_lasso <- c(num.proxy_lasso, length(proxy_lasso))
  names(num.proxy_lasso)[i+2*a] <- paste0("OR.data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.OR.", i)
  assign(proxy_lasso.i, proxy_lasso)
  num.proxy_lasso.i <- paste0("num.proxy_lasso.OR.", i)
  assign(num.proxy_lasso.i, length(proxy_lasso))
  sum.RD_lasso.i <- paste0("sum.RD_lasso.OR.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

@@

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_lasso
mean(num.proxy_lasso[complete.cases(num.proxy_lasso)])
```

@@

# check proxy selected by lasso for each data, print:
#   proxy_lasso.n, proxy_lasso.ER.n, or proxy_lasso.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_lasso.1
proxy_lasso.ER.3

# check number of proxy selected by lasso for each data, print:
#   num.proxy_lasso.n, num.proxy_lasso.ER.n, or num.proxy_lasso.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_lasso.1
num.proxy_lasso.OR.3
```

### 2024-08-08 sim_4_enet/simResults_enet.Rmd
simulation results .RMD file added & edited

---
title: "simResults_enet"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

RD_enet <- data.frame(RD = numeric(),
                       SE = numeric())
```

@@

  RD_enet[i,] <- sum.RD_enet
  rownames(RD_enet)[i] <- paste0("data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

@@

  RD_enet[i+a,] <- sum.RD_enet
  rownames(RD_enet)[i+a] <- paste0("ER.data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.ER.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.ER.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

@@

  RD_enet[i+2*a,] <- sum.RD_enet
  rownames(RD_enet)[i+2*a] <- paste0("OR.data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.OR.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.OR.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

@@

@@

# check proxy selected by enet for each data, print:
#   proxy_enet.n, proxy_enet.ER.n, or proxy_enet.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_enet.1
proxy_enet.ER.3
```

>>>>

---
title: "simResults_enet"
output: html_document
---

@@

RD_enet <- data.frame(RD = numeric(),
                       SE = numeric())

num.proxy_enet <- c()
```

@@

  RD_enet[i,] <- sum.RD_enet
  rownames(RD_enet)[i] <- paste0("data.", i, "_enet")
  num.proxy_enet <- c(num.proxy_enet, length(proxy_enet))
  names(num.proxy_enet)[i] <- paste0("data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.", i)
  assign(proxy_enet.i, proxy_enet)
  num.proxy_enet.i <- paste0("num.proxy_enet.", i)
  assign(num.proxy_enet.i, length(proxy_enet))
  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

@@

  RD_enet[i+a,] <- sum.RD_enet
  rownames(RD_enet)[i+a] <- paste0("ER.data.", i, "_enet")
  num.proxy_enet <- c(num.proxy_enet, length(proxy_enet))
  names(num.proxy_enet)[i+a] <- paste0("data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.ER.", i)
  assign(proxy_enet.i, proxy_enet)
  num.proxy_enet.i <- paste0("num.proxy_enet.ER.", i)
  assign(num.proxy_enet.i, length(proxy_enet))
  sum.RD_enet.i <- paste0("sum.RD_enet.ER.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

@@

  RD_enet[i+2*a,] <- sum.RD_enet
  rownames(RD_enet)[i+2*a] <- paste0("OR.data.", i, "_enet")
  num.proxy_enet <- c(num.proxy_enet, length(proxy_enet))
  names(num.proxy_enet)[i+2*a] <- paste0("data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.OR.", i)
  assign(proxy_enet.i, proxy_enet)  
  num.proxy_enet.i <- paste0("num.proxy_enet.OR.", i)
  assign(num.proxy_enet.i, length(proxy_enet))
  sum.RD_enet.i <- paste0("sum.RD_enet.OR.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

@@

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_enet
mean(num.proxy_enet[complete.cases(num.proxy_enet)])
```

@@

# check proxy selected by enet for each data, print:
#   proxy_enet.n, proxy_enet.ER.n, or proxy_enet.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_enet.1
proxy_enet.ER.3

# check number of proxy selected by enet for each data, print:
#   num.proxy_enet.n, num.proxy_enet.ER.n, or num.proxy_enet.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_enet.1
num.proxy_enet.OR.4
```

### 2024-08-08 sim_5_svm/simResults_svm.Rmd
simulation results .RMD file added & edited

---
title: "simResults_svm"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

RD_svm <- data.frame(RD = numeric(),
                       SE = numeric())
```

@@

  RD_svm[i,] <- sum.RD_svm
  rownames(RD_svm)[i] <- paste0("data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.", i)
  assign(proxy_svm.i, proxy_svm)
  sum.RD_svm.i <- paste0("sum.RD_svm.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

@@

  RD_svm[i+a,] <- sum.RD_svm
  rownames(RD_svm)[i+a] <- paste0("ER.data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.ER.", i)
  assign(proxy_svm.i, proxy_svm)
  sum.RD_svm.i <- paste0("sum.RD_svm.ER.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

@@

  RD_svm[i+2*a,] <- sum.RD_svm
  rownames(RD_svm)[i+2*a] <- paste0("OR.data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.OR.", i)
  assign(proxy_svm.i, proxy_svm)
  sum.RD_svm.i <- paste0("sum.RD_svm.OR.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

@@

@@

# check proxy selected by svm for each data, print:
#   proxy_svm.n, proxy_svm.ER.n, or proxy_svm.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_svm.1
proxy_svm.ER.3
```

>>>>

---
title: "simResults_svm"
output: html_document
---

@@

RD_svm <- data.frame(RD = numeric(), SE = numeric())

num.proxy_svm <- c()
```

@@

  RD_svm[i,] <- sum.RD_svm
  rownames(RD_svm)[i] <- paste0("data.", i, "_svm")
  num.proxy_svm <- c(num.proxy_svm, length(proxy_svm))
  names(num.proxy_svm)[i] <- paste0("data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.", i)
  assign(proxy_svm.i, proxy_svm)
  num.proxy_svm.i <- paste0("num.proxy_svm.", i)
  assign(num.proxy_svm.i, length(proxy_svm))
  sum.RD_svm.i <- paste0("sum.RD_svm.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

@@

  RD_svm[i+a,] <- sum.RD_svm
  rownames(RD_svm)[i+a] <- paste0("ER.data.", i, "_svm")
  num.proxy_svm <- c(num.proxy_svm, length(proxy_svm))
  names(num.proxy_svm)[i+a] <- paste0("ER.data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.ER.", i)
  assign(proxy_svm.i, proxy_svm)
  num.proxy_svm.i <- paste0("num.proxy_svm.ER.", i)
  assign(num.proxy_svm.i, length(proxy_svm))
  sum.RD_svm.i <- paste0("sum.RD_svm.ER.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

@@

  RD_svm[i+2*a,] <- sum.RD_svm
  rownames(RD_svm)[i+2*a] <- paste0("OR.data.", i, "_svm")
  num.proxy_svm <- c(num.proxy_svm, length(proxy_svm))
  names(num.proxy_svm)[i+2*a] <- paste0("OR.data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.OR.", i)
  assign(proxy_svm.i, proxy_svm)
  num.proxy_svm.i <- paste0("num.proxy_svm.OR.", i)
  assign(num.proxy_svm.i, length(proxy_svm))
  sum.RD_svm.i <- paste0("sum.RD_svm.OR.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

@@

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_svm
mean(num.proxy_svm[complete.cases(num.proxy_svm)])
```

@@

# check proxy selected by svm for each data, print:
#   proxy_svm.n, proxy_svm.ER.n, or proxy_svm.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_svm.1
proxy_svm.ER.3

# check number of proxy selected by svm for each data, print:
#   num.proxy_svm.n, num.proxy_svm.ER.n, or num.proxy_svm.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_svm.1
num.proxy_svm.OR.3
```

### 2024-08-08 sim_6_ga/simResults_ga.Rmd
simulation results .RMD file added & edited

---
title: "simResults_ga"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

RD_ga <- data.frame(RD = numeric(),
                       SE = numeric())
```

@@

  RD_ga[i,] <- sum.RD_ga
  rownames(RD_ga)[i] <- paste0("data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.", i)
  assign(proxy_ga.i, proxy_ga)
  sum.RD_ga.i <- paste0("sum.RD_ga.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

@@

  RD_ga[i+a,] <- sum.RD_ga
  rownames(RD_ga)[i+a] <- paste0("ER.data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.ER.", i)
  assign(proxy_ga.i, proxy_ga)
  sum.RD_ga.i <- paste0("sum.RD_ga.ER.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

@@

  RD_ga[i+2*a,] <- sum.RD_ga
  rownames(RD_ga)[i+2*a] <- paste0("OR.data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.OR.", i)
  assign(proxy_ga.i, proxy_ga)
  sum.RD_ga.i <- paste0("sum.RD_ga.OR.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

@@

@@

# check proxy selected by ga for each data, print:
#   proxy_ga.n, proxy_ga.ER.n, or proxy_ga.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_ga.1
proxy_ga.ER.3
```

>>>>

---
title: "simResults_ga"
output: html_document
---

@@

RD_ga <- data.frame(RD = numeric(), SE = numeric())

num.proxy_ga <- c()
```

@@

  RD_ga[i,] <- sum.RD_ga
  rownames(RD_ga)[i] <- paste0("data.", i, "_ga")
  num.proxy_ga <- c(num.proxy_ga, length(proxy_ga))
  names(num.proxy_ga)[i] <- paste0("data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.", i)
  assign(proxy_ga.i, proxy_ga)
  num.proxy_ga.i <- paste0("num.proxy_ga.", i)
  assign(num.proxy_ga.i, length(proxy_ga))
  sum.RD_ga.i <- paste0("sum.RD_ga.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

@@

  RD_ga[i+a,] <- sum.RD_ga
  rownames(RD_ga)[i+a] <- paste0("ER.data.", i, "_ga")
  num.proxy_ga <- c(num.proxy_ga, length(proxy_ga))
  names(num.proxy_ga)[i+a] <- paste0("ER.data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.ER.", i)
  assign(proxy_ga.i, proxy_ga)
  num.proxy_ga.i <- paste0("num.proxy_ga.ER.", i)
  assign(num.proxy_ga.i, length(proxy_ga))
  sum.RD_ga.i <- paste0("sum.RD_ga.ER.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

@@

  RD_ga[i+2*a,] <- sum.RD_ga
  rownames(RD_ga)[i+2*a] <- paste0("OR.data.", i, "_ga")
  num.proxy_ga <- c(num.proxy_ga, length(proxy_ga))
  names(num.proxy_ga)[i+2*a] <- paste0("OR.data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.OR.", i)
  assign(proxy_ga.i, proxy_ga)
  num.proxy_ga.i <- paste0("num.proxy_ga.OR.", i)
  assign(num.proxy_ga.i, length(proxy_ga))
  sum.RD_ga.i <- paste0("sum.RD_ga.OR.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

@@

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_ga
mean(num.proxy_ga[complete.cases(num.proxy_ga)])
```

@@

# check proxy selected by ga for each data, print:
#   proxy_ga.n, proxy_ga.ER.n, or proxy_ga.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_ga.1
proxy_ga.ER.3

# check number of proxy selected by ga for each data, print:
#   num.proxy_ga.n, num.proxy_ga.ER.n, or num.proxy_ga.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_ga.1
num.proxy_ga.OR.3
```

### 2024-08-08 sim_7_xgboost/simResults_xgboost.Rmd
simulation results .RMD file added & edited

---
title: "simResults_xgboost"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

RD_xgboost <- data.frame(RD = numeric(), SE = numeric())
```

@@

  RD_xgboost[i,] <- sum.RD_xgboost
  rownames(RD_xgboost)[i] <- paste0("data.", i, "_xgboost")

  proxy_xgboost.i <- paste0("proxy_xgboost.", i)
  assign(proxy_xgboost.i, proxy_xgboost)
  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.", i)
  assign(sum.RD_xgboost.i, sum.RD_xgboost)
}
```

@@

  RD_xgboost[i+a,] <- sum.RD_xgboost
  rownames(RD_xgboost)[i+a] <- paste0("ER.data.", i, "_xgboost")

  proxy_xgboost.i <- paste0("proxy_xgboost.ER.", i)
  assign(proxy_xgboost.i, proxy_xgboost)
  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.ER.", i)
  assign(sum.RD_xgboost.i, sum.RD_xgboost)
}
```

@@

  RD_xgboost[i+2*a,] <- sum.RD_xgboost
  rownames(RD_xgboost)[i+2*a] <- paste0("OR.data.", i, "_xgboost")

  proxy_xgboost.i <- paste0("proxy_xgboost.OR.", i)
  assign(proxy_xgboost.i, proxy_xgboost)
  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.OR.", i)
  assign(sum.RD_xgboost.i, sum.RD_xgboost)
}
```

@@

@@

# check proxy selected by xgboost for each data, print:
#   proxy_xgboost.n, proxy_xgboost.ER.n, or proxy_xgboost.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_xgboost.1
proxy_xgboost.ER.3
```

>>>>

---
title: "simResults_xgboost"
output: html_document
---

@@

RD_xgboost <- data.frame(RD = numeric(), SE = numeric())

num.proxy_xgboost <- c()
```

@@

  RD_xgboost[i,] <- sum.RD_xgboost
  rownames(RD_xgboost)[i] <- paste0("data.", i, "_xgboost")
  num.proxy_xgboost <- c(num.proxy_xgboost, length(proxy_xgboost))
  names(num.proxy_xgboost)[i] <- paste0("data.", i, "_xgboost")

  proxy_xgboost.i <- paste0("proxy_xgboost.", i)
  assign(proxy_xgboost.i, proxy_xgboost)
  num.proxy_xgboost.i <- paste0("num.proxy_xgboost.", i)
  assign(num.proxy_xgboost.i, length(proxy_xgboost))
  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.", i)
  assign(sum.RD_xgboost.i, sum.RD_xgboost)
}
```

@@

  RD_xgboost[i+a,] <- sum.RD_xgboost
  rownames(RD_xgboost)[i+a] <- paste0("ER.data.", i, "_xgboost")
  num.proxy_xgboost <- c(num.proxy_xgboost, length(proxy_xgboost))
  names(num.proxy_xgboost)[i+a] <- paste0("ER.data.", i, "_xgboost")

  proxy_xgboost.i <- paste0("proxy_xgboost.ER.", i)
  assign(proxy_xgboost.i, proxy_xgboost)
  num.proxy_xgboost.i <- paste0("num.proxy_xgboost.ER.", i)
  assign(num.proxy_xgboost.i, length(proxy_xgboost))
  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.ER.", i)
  assign(sum.RD_xgboost.i, sum.RD_xgboost)
}
```

@@

  RD_xgboost[i+2*a,] <- sum.RD_xgboost
  rownames(RD_xgboost)[i+2*a] <- paste0("OR.data.", i, "_xgboost")
  num.proxy_xgboost <- c(num.proxy_xgboost, length(proxy_xgboost))
  names(num.proxy_xgboost)[i+2*a] <- paste0("OR.data.", i, "_xgboost")

  proxy_xgboost.i <- paste0("proxy_xgboost.OR.", i)
  assign(proxy_xgboost.i, proxy_xgboost)
  num.proxy_xgboost.i <- paste0("num.proxy_xgboost.OR.", i)
  assign(num.proxy_xgboost.i, length(proxy_xgboost))
  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.OR.", i)
  assign(sum.RD_xgboost.i, sum.RD_xgboost)
}
```

@@

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_xgboost
mean(num.proxy_xgboost[complete.cases(num.proxy_xgboost)])
```

@@

# check proxy selected by xgboost for each data, print:
#   proxy_xgboost.n, proxy_xgboost.ER.n, or proxy_xgboost.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_xgboost.1
proxy_xgboost.ER.3

# check number of proxy selected by xgboost for each data, print:
#   num.proxy_xgboost.n, num.proxy_xgboost.ER.n, or num.proxy_xgboost.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_xgboost.1
num.proxy_xgboost.OR.3
```

### 2024-08-08 sim_8_rf/simResults_rf.Rmd
simulation results .RMD file added & edited

---
title: "simResults_rf"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1

@@

  # found some id != idx
  data$id <- data$idx

>>>>

---
title: "simResults_rf"
output: html_document
---

@@

@@

  # found some id != idx
  data$idx <- data$id
